Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-16 TEBenchmarkPaper/article.tex
Sections

Section \ref{sec:background} describes MTE and the conjecture generation problem
in more detail, along with existing approaches and their evaluation
methodologies. We explain our proposal for a more general benchmark in section
\ref{sec:proposal} whilst section \ref{sec:application} shows the results when
applied to existing MTE tools. Analysis of these results is given in section
\ref{sec:discussion} and concluding remarks in section \ref{sec:conclusion}.

>>>>

We introduce the conjecture generation problem in more detail, along with the
difficulty of comparing existing solutions, in $\S$\ref{sec:background}. In
$\S$\ref{exploration-versus-formation} we give a history of the MTE field, and
its close cousin Automated Theory Formation (ATF), describing a variety of
existing approaches and clarifying the diverse terminology found in the
literature. We explain our proposal for a more general benchmark in
$\S$\ref{sec:proposal} and demonstrate its application to existing MTE tools
in $\S$\ref{sec:application}. Issues facing our approach, and the field in
general, are discussed in $\S$\ref{sec:discussion} and concluding remarks
are given in $\S$\ref{sec:conclusion}.
